Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-29 chapters/introduction/introduction.tex
main contribution first paragraph

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint, we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it is reflected by the scene layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with detected vanishing points. We
  present the algorithm details in \chapref{fasthorizon}.  \newline

@@

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of constraint function, feed the aerial
  image of a given location and orientation set to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency of these two as
  the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

@@

\subsection{Geo-Calibration for Feature Learning}
Our methods also provide another way to dealing with the challenges of
lacking manual annotations during DNN training. By learning to
geo-calibrate a camera, we believe the networks are able to learn
high-level image representations. This belief comes from the fact that
the geo-calibration information of a camera encodes semantic
information because it is closely related to the appearances of the
scene.
We explore two types of learning techniques for high-level feature
extraction: 1) semantic segmentation of the aerial imagery with
ground-level annotations which is plentiful, and 2) geo-temporal
features with automatically annotated geographic locations and time.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning:}
  Most current machine learning methods study problems involving the
  ground imagery. There exist many annotated dataset of the ground
  imagery while much fewer of the aerial imagery. 
  In \chapref{crosstransf}, we proposed a
  method to learn to semantically segment aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in cross-view pairs. 
  In this work, we try to transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
  which have been successfully applied in monocular depth estimation,
  our network learns geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  \newline

>>>>

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint, we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it can be explicitly estimated from the scene
  layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with detected vanishing points. We
  present the algorithm details in \chapref{fasthorizon}.  \newline

@@

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of the constraint function, feed the aerial
  image of a given location and orientation set to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency of these two as
  the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

@@

\subsection{Geo-Calibration for Image Feature Learning}
Full supervision algorithms are powerful tools to learn useful image
features. However, full supervision algorithms requires large number
of annotated data, which in many cases are either not available or
financially infeasible to obtain. On the other hand, images with free
annotations like time and locations are plentiful on the Internet.
To use these image resources for image feature learning, 
we explore two types of learning techniques that uses time and
locations as annotations: 1) {\em ground-to-aerial segmentation}, and 2)
{\em geo-temporal feature learning} with time/location tagged images.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Segmentation:}
  Most current machine learning methods study problems involving the
  ground imagery. There exist many annotated dataset of the ground
  imagery while much fewer of the aerial imagery. 
  In \chapref{crosstransf}, we proposed a
  method to learn to semantically segment aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in cross-view pairs. 
  In this work, we try to transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
  which have been successfully applied in monocular depth estimation,
  our network learns geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  \newline

### 2018-08-29 chapters/introduction/junk.tex
background geo-calibration
more changes on background.
geo-calibration feature learning
before fine location and orientation section
main contribution first paragraph

>>>>

%However, recognizing the geo-location and geo-orientation of an
%arbitrary outdoor image is an extremely challenging task.  Many
%methods have been proposed; the most common approach is to build a
%large database of images with known location and localize a query
%image using either local~\cite{li2010location,schindler2008detecting}
%or global~\cite{hays2008im2gps,doersch2012what} image features. 
%This approach is not applicable when no nearby ground-level imagery
%exists in the reference database, such as when the image was not
%captured near a popular tourist destination.  Even when reference
%imagery is available, the appearance of the objects may not be
%visually distinctive, for example a train track or a body of water.

%Cross-view image pair is the basic element for ground-to-aerial
%geo-calibration. It consists of a ground-level image and an overhead
%image at the same location. In some cases, two images may also be aligned
%in orientation.

Though full supervision work well in many applications, there are
exponentially more image resources without manual annotation (cell
phone imagery, YouTube videos\etc), which show a huge potential for
visual feature learning.

%Imagine a human geo-localizing a camera from an image it took, one
%could roughly guess where a photo was taken when she sees an polar
%bear on an iceberg. In this scenario, learning high-level
%features becomes a necessary process of abstracting visual hints to
%localize the camera.

Our methods also provide another way to dealing with the challenges of
lacking manual annotations during DNN training. By learning to
geo-calibrate a camera, we believe the networks are able to learn
high-level image representations. This belief comes from the fact that
the geo-calibration information of a camera encodes semantic
information because it is closely related to the appearances of the
scene.
